---
title: "miniproject3"
author: "Nikki Liu""Yingqi Zheng""Jingjing Hu"
date: "11/15/2017"
output: html_document
---

##Westerns Over Time

```{r, message = FALSE}
library(dplyr)
library(mosaic)
library(tidyverse)
library(readr)
library(ggplot2)
library(scales)
Western_1117 <- read_csv("~/SDS192_mp3_zhl/Western_1120.csv")
```

```{r}
library(mdsr)
library(RMySQL)
db <- dbConnect_scidb(dbname = "imdb")
Western_1117 <- db %>%
  dbGetQuery("SELECT info_type_id, movie_info.movie_id, info, keyword, title.phonetic_code, production_year, title
 FROM imdb.title
 JOIN imdb.movie_info ON movie_info.movie_id = title.id
 JOIN imdb.keyword ON imdb.title.phonetic_code = keyword.phonetic_code
 HAVING info_type_id = 3 AND info = 'Western';")
```

In SQL, me merged movie_info, title and keyword to get the information we need (title, keyword and production year). We also used the index column of info_type_id = 3 to speed things up.


#Between 1900 and 2015, when and how has Western film production peaked and ebbed? 

```{r}
peakWestern <- Western_1117 %>%
  filter(production_year<=2015) %>%
  filter(production_year>=1900)%>%
  group_by(production_year) %>%
  summarize(number = n_distinct(movie_id)) %>%
  arrange(desc(number))
```

n_distinct(movie_id)

Western movie set its story in later half of 19th centrury in the American Old West and always centered a cowboy or gunfighter hero on horseback saving the homestead from savages or finding the treasure in the mountains.(Agresta, 2013) They have long been cherished by American audiences throughout time, seen as representitaves of American culture and American Dreams. However, Western as a genre is experiencing a decline over recent years and was substituted by other genre, for example, superheroes, as the most popular movies in the US. In this project, we explore the quantitative trend of the production of Western movies from 1900 to 2015, and analyse the trend by examining simultaneous history events.


```{r}
peakWestern %>%
  ggplot(aes(y = number, x = production_year)) +
  geom_bar(stat = "identity") +
  scale_x_discrete(breaks = c(1900, 1910, 1920, 1930, 1940, 1950, 1960, 1970, 1980, 1990, 2000, 2010)) +
  labs(x = "Production Year", y = "Number of Western Movies", title = "Number of Western Movies Between 1900 and 2015") + geom_bar(data = subset(peakWestern, number == max (number)), aes(x = production_year, y = number), fill = "red", stat = "identity") +
  geom_text(data = subset(peakWestern, number == max (number)), aes(x = production_year, y = number, label = production_year), hjust = -0.2) +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_bar(data = subset(peakWestern, number == min (number)), aes(x = production_year, y = number), fill = "blue", stat = "identity") 
```

As the graph shows, the production of Western movies peaked in the period of 1910 to 1930 and around 2010. The number of Western movies then quickly fall in the beginning of 1930s and reached a low rate of production in 1980s and 1990s.

The development and blooming of Hollywood may count for the peak of Western movies in 1910 to 1930(Dirks, ). According to Dirks' article, Hollywood was a small corporation before 1910. In the following ten years, it grew rapidly as long as its film production. By 1915, 60% of film production came from Hollywood.At that time, Western was the most popular Hollywood genre. The bloom of Hollywood continued in the 1920s as long as the bloom of Western movies.

The Great Depression came in the 1930s and hit the film production so hard that it reduced production rates in almost all genres, including Western (University of Minnesota, ). World War II influenced the film market badly in the early 1940s and the production drop even further.The production rate kept low as television expanded its market.

The 1980s and the 1990s were the decades when the total production of films reached the lowest point in the US, where was the Western movies mostly from.(Pollock, 2008) They were also the period when the last fans of Western movies from the 1930s, or the last generation with a memory of blooming Western movies, grown old and not willing to go out for a movie.(Agresta, 2013) The market further shrank and the production went to the lowest point in the history.

The film production raised at the start of the new century and kept rising in the following decade, along with the production of Western movies.

Dirks: http://www.filmsite.org/filmh.html

U of Mennisota: https://quod.lib.umich.edu/h/humfig/11217607.0004.202/--explaining-american-hypocrisy?rgn=main;view=fulltext

Pollock: http://rufuspollock.com/2008/10/17/filmmovie-production-over-time/

Agresta: https://www.theatlantic.com/entertainment/archive/2013/07/how-the-western-was-lost-and-why-it-matters/278057/



#What might account for this, and does the IMDB define a Western in the 1950 in the same way as it does in 2000?

We think that the definition of Western films can be reflected by frequent keywords of movie contents at different periods of time. Keywords are selected by IMDB to indicate the prominent feature of each individual film, and they imply people's understanding of "what a Western film is". Therefore, we think the change of movies' keywords reveals the alternation of people's perception of Western films.

In order to track the dynamic movement of keywords' appearance in IMDB database, we sum up the time each keyword appears in each decade between 1950 and 2000. Due to the enormous quantity and great diversity of keywords, we decide to look at keywords with relatively high frequency, and thus more importance to the defintion of Western films. We only select those keywords that appear more than 2 times in each decade.

```{r}
options("scipen"=999, "digits"=4)
Western_decade <- Western_1117 %>%
  mutate(decade = cut(as.numeric(production_year), seq(from = 1950, to = 2000, by = 10), dig.lab = 5,  include.lowest = TRUE, include.highest = FALSE)) %>%
  filter(decade != 'NA')%>%
  group_by(keyword, decade) %>%
  summarise(number = n())%>%
  filter(number >= 3)
Western_decade
```

We plot those keywords on the x-axis and number of appearance on the y-axis, and we use color and shape to differentiate each decade. 

```{r}
plot1 <- ggplot(aes(x=keyword, y=number), data=Western_decade) +
  geom_point(aes(shape = decade, color = decade))+
  scale_y_continuous(breaks = c(2,3,4,5,6,7,8,9,10,11,12,13,14,15))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Western Film Keywords Frequency Change Over Decades")+
  theme(plot.title = element_text(hjust = 0.5))
plot1
```

Besides the frequency of keywords, we also look at the variety of keywords that appear in the database. This is an useful metric to see the wide range of Western movie made in each decade. As we can see from the numbers, the 1950s and 1960s have the widest range of keywords for Western movies.

```{r}
Western_defrange <- Western_1117 %>%
  mutate(decade = cut(as.numeric(production_year), seq(from = 1950, to = 2000, by = 10), dig.lab = 5, include.lowest = TRUE, include.highest = FALSE)) %>%
  filter(decade != 'NA') %>%
  group_by(decade) %>%
  summarise(movierange = length(unique(keyword)))
Western_defrange
```


Our observation of trends in Western films is consistent with C.J. Perry's viewpoints in the article "The Evolution of the Western Genre". 

As we can see from the graph, many keywords appear 3 or 4 times in 1950s, and the keyword with the highest frequency is 'gay-minister' (11 times), followed by school-shooting (8 times) and face-sitting (6 times), which means that there was no much variation in the basic plots. The total number of unique keywords (no matter how many times each keyword appears) in 1950s is 127, and it is the highest in the fifty years we are looking at. These observations correspond to Perry's depiction of western films in 1950s. At that time, western movies often had similar plots about an iconic white man, such as John Wayne in the "The Searchers", involving in different kinds of violent events. 

According to the graph, from 1961 to 1970 (green triangles), there are more keywords that appear more than twice. Among them, 'Southern-accent' (14 times), 'blood-brother' and 'bullet proof glass' (7 times), and 'blood spurting' (6 times). Note that the keyword 'Southern-accent' has the highest frequency from 1950 to 2000. There are more movies associated with the South compared to movies from the previous period, and the violent scenes seem more frequent.  These changes are also mentioned in Perry's article. He emphasizes that the provalence of TV at that period resulted in broader audience base that demanded more diverse storytelling styles of western films, among which family drama, such as "the wild wild west", was one of the most popular ones. This was proved by the frequent appearance of the keyword "bloody brother".  

From 1971 to 1980 (blue squares), as we can see in the graph, there are less keywords that appear more than twice compared to that of the two previous periods and the number of western films produced started decreasing more drastically. The impact of Southern culture in Western movies is still prevalent because the keyword 'Southern accent' still has the highest frequency (7 times). There are also a few keywords that appear 4 times, including 'blood brothers', 'bullet proof glass', 'caiman', 'china' and 'jackass'. The 1970s seem to be strongly influenced by the trends of 1960s, as the top keywords in 1960s are still prevalent in 1970s. The appearance of more varying themes is consistant to what Perry pointed out in the article. Traditional way of film making was being assaulted and young filmmakers, such as Sam Pekinpah and Sergio Leone, were trying to push the envelope with other types of storytellings. Some of the new themes mentioned by Perry included aging, skewed morality, and racism, and there were more satirizing than battling in the new ways of storytellings. These evolutions led to another peak at this period as we can see in the histogram plot above.

From 1981 to 1990, according to the graph, there is no keyword that appears more than twice! We think that it might because the Western films of this period is very diverse (no traits of concentration around some major topics) and the decline in number of Western films. In fact, there are only 27 keywords in this period, which is the lowest from 1950 to 2000. Perry also confirms this in the article that the western films was vanishing during 80s and some famous series, such as Eastwood, stopped making new ones.

From 1991 to 2000, there is only one keyword that appears more than twice, which is the 'second city' (4 times). Neverthles, there were in total 45 keywords in this period, signifing an increase in the production of Western films in this period. Perry also mentioned that it was not until 1990s that western films started coming back to the screen again, with more entertaining purposes. 

In a word, what we can observed in the graphs above is corresponding with what was going on in the western filming industry from 1950 to 2000 as discussed in J.C. Perry's article.

Github Link: https://github.com/ArthiiNW/SDS192_mp3_zhl
