---
title: "miniproject3"
author: "Nikki Liu""Yingqi Zheng""Jingjing Hu"
date: "11/15/2017"
output: html_document
---

```{r, message = FALSE}
library(dplyr)
library(mosaic)
library(tidyverse)
library(readr)
library(ggplot2)
library(scales)
Western_1117 <- read_csv("~/SDS192_MP3/Western_1117.csv")
```

```{r}
Western <- Western_1117 %>% 
  filter(production_year == c(1950,2000))%>%
  group_by(keyword, production_year) %>%
  summarise(number = n())
Western
```

```{r}
options("scipen"=999, "digits"=4)
Western_decade <- Western_1117 %>%
  mutate(decade = cut(as.numeric(production_year), seq(from = 1950, to = 2000, by = 10), dig.lab = 5,  include.lowest = TRUE, include.highest = FALSE)) %>%
  filter(decade != 'NA')%>%
  group_by(keyword, decade) %>%
  summarise(number = n())%>%
  filter(number >= 3)
Western_decade
```
  scale_fill_gradient(low = "blue", high = "red", name = 'Decades', labels = comma)+
aes(color = production_year)
```{r}
plot1 <- ggplot(aes(x=keyword, y=number), data=Western_decade) +
  geom_point(aes(shape = decade, color = decade))+
  scale_y_continuous(breaks = c(2,3,4,5,6,7,8,9,10,11,12,13,14,15))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Western Film Keywords Frequency Change Over Decades")+
  theme(plot.title = element_text(hjust = 0.5))
plot1
```
```{r}
Western_defrange <- Western_1117 %>%
  mutate(decade = cut(as.numeric(production_year), seq(from = 1950, to = 2000, by = 10), dig.lab = 5, include.lowest = TRUE, include.highest = FALSE)) %>%
  filter(decade != 'NA')%>%
  group_by(decade) %>%
  summarise(number = n()) 
  filter(number >= 3)%>%
Western_defrange
```


We think that the definition of Western films can be reflected by frequent keywords of movie contents at different periods of time. Keywords are selected by IMDB to indicate the prominent feature of each individual film, and they imply people's understanding of "what a Western film is". Therefore, we think the change of movies' keywords reveals the alternation of people's perception of Western films.

In order to track the dynamic movement of keywords' appearance in IMDB database, we sum up the time each keyword appears in each decade between 1950 and 2000. Due to the enormous quantity and great diversity of keywords, we decide to look at keywords with relatively high frequency, and thus more importance to the defintion of Western films. We only select those keywords that appear more than 2 times in each decade, and we plot those keywords on the x-axis and number of appearance on the y-axis, and we use color and shape to differentiate each decade. 

